Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-30 draft/paper1_rachel.tex
Edit final sample 2

\def\etal{{\ et al.~}}
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}
\def\redm{\texttt{redMaPPer}}
\def\cmodel{\texttt{cModel}}
% Samples
\def\rbcg{\texttt{cenHighMh}}
\def\nbcg{\texttt{cenLowMh}}
\def\redbcg{{$\lambda \ge 30$}}
\def\nonbcg{{$\lambda < 20$}}
% Mass related 
\def\mstar{{$M_{\star}$}}
\def\mhalo{{$M_{\mathrm{halo}}$}}
\def\logms{{$\log (M_{\star}/M_{\odot})$}}
\def\logmh{{$\log (M_{\mathrm{halo}}/M_{\odot})$}}

@@

    With the help of the Stripe82 Massive Galaxy Catalog (\texttt{S82-MGC},
    \citealt{Bundy2015}
    )\footnote{http://www.ucolick.org/$~$kbundy/massivegalaxies/s82-mgc.html}, 
    we investigate the \mstar{} completeness of our samples. 
    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the United 
    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; 
    \citealt{Lawrence2007}). 
    Comparing to normal SDSS images, the deeper photometry and better photo-$z$s 
    from \texttt{S82-MGC} make this sample complete to \logms{}$\geq 11.2$ at $z<0.7$ 
    which makes it sufficient to evaluate the completeness of our HSC sample.   
	By comparing with the \texttt{S82-MGC} sample (\citealt{Bundy2015}), 
	\citet{Leauthaud2016} have measured the \mstar{} completeness of the combined BOSS 
	and SDSS samples. 
    They estimate that the BOSS spec-$z$ sample, which is the main source of redshifts 
    for our sample, is about 80\% complete at 
    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. The GAMA survey is 80\% complete down to 
    $10^{10.8}$\msun{} at $z{\sim} 0.3$, but is only 80\% complete to 
    $10^{12.0}$\msun{} at $z{\sim} 0.5$ according to \citet{Taylor2011} (e.g.\ 
    their Fig.~6).

@@

    We use \texttt{v5.10} of the \redm{} cluster  catalog
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
    These authors have developed a well-tested red-sequence cluster finder that has 
    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
    their associated membership probabilities. 
    Details about the performance of the \redm{}~cluster catalog can be found in 
    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}.

    Several studies have published calibrations between the \redm{}~richness estimate, 
    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
    Melchior2016}). 
    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
    Therefore the central galaxies of these \redm{} clusters\footnote{We only use the 
    central galaxies with $P_{\mathrm{CEN}} \geq 0.7$} form a sample of massive central 
    galaxies that live in massive halos as described above.
\rachel{Intrinsic scatter in \mhalo{} at fixed $\lambda$ is pretty big, though, so we should be careful about this assertion.}
Such information is also very useful in studying the relationship between galaxy
    structure and environment (Huang\etal in prep.).
%% ------------------------------------------------------------------------------------ %%

@@

    As the next step, we want to construct a sample of central galaxies living in halos 
    with \logmh{}$<14.0$. 
    To achieve this, we identify and remove all galaxies within a cylindrical region 
    around all \redm{} clusters. 
    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
    set to twice the value of the photometric redshift uncertainty of each cluster ().
\rachel{Need to fill in empty parenthesis in previous sentence.}

    We convert $\lambda$ of each cluster to $M_{\mathrm{halo}}$ using the calibration 
    of \citet{Simet2016} and we use the mass-concentration relation from 
    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. 
    At $0.3 < z < 0.5$, the uncertainty of photo-$z$ is between 0.015 to 0.025, and 
    is enough to exclude cluster members.

    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
    in our sample will be dominated by central galaxies living in halos with 
    \logmh{}$< 14.0$. 
    We will refer to this sample of \textbf{galaxies in less 
    massive halos} as the \nbcg{} sample. Because we have rejected satellites in \redm{} clusters, and because above our galaxy mass cut most satellites reside in halos with $\log{(M_{halo})}>14$ (e.g. \citealt{Reid2014, 
    Hoshino2015, Saito2016, vanUitert2016}), galaxies in the \nbcg{} sample should  be dominated by central galaxies.
    \rachel{There is a statistical distribution of halo masses that satellites at this stellar mass live in, based on the papers you cited; can you say more quantitatively what fraction you expect to be satellites in less massive halos?  Right now it all sounds kind of hand-wavey.}

@@

In this paper, we have only measured light profiles for central galaxies. Also,  we cannot extract  a 1-D profile for xxxxxx\% of galaxies (because contamination from neighbouring galaxies is too severe). These two effects will lead to a ${\sim}20$\% uncertainty in  the amplitude of our SMF.  \rachel{Mass-dependent, or really 20\% at all masses?} These are limitations that we are currently working to address and a forthcoming paper will  address them. Our goal in this paper is therefore not  to  attempt a detailed comparison between different SMFs
    \citep[e.g.,][]{Bernardi2013, Bernardi2017}. Instead, our goal in this section is more simply to characterize the  impact of various \mstar{} measurements  on the high-mass end of the SMF.

@@

        \item The SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
            \citep{Leauthaud2016} where \mstar{} is derived using 
            \texttt{iSEDfit} on PSF-corrected aperture photometry from 
            \texttt{S82}. They adopt the same IMF, dust model, and star-formation model as we do, but use the \texttt{BC03} model. Based on the test results from Appendix \ref{app:sed}, we shift the \citet{Leauthaud2016} SMF by 0.08 dex to add their data to Figure~\ref{fig:smf}.      
        \item The SMF derived from a SDSS-\textit{GALEX} sample of $z{\sim} 0.1$ 
            galaxies from \citet{Moustakas13}.  Total luminosities from \citet{Moustakas13} are based on SDSS \cmodel{} magnitude. 
            They use a \m2l{} that is derived via SED fitting using \texttt{iSEDfit} with similar 
            assumptions as here.
        \item The observed SMF for $z{\sim} 0.1$ SDSS galaxies from 
            \citet{Bernardi2017}.  Total luminosities in  \citet{Bernardi2017} are based on 2-D \texttt{SerExp} models 
            (\ser{}$+$ Exponential disk model; integrated to infinity) that 
            recover more flux compared to SDSS \cmodel{} magnitudes 
            (\citealt{Bernardi2013, Meert2015}). 
            They use a  \m2l{} that is adopted from the SED fitting results from the ``dusty'' 
            model in \citet{Mendel2014}.  \alexie{CLARIFY HERE SSp model}.   
    \end{itemize}

@@

    Finally, we also compare with the predicted median \mden{} profile of central 
    galaxies in massive halos ($13.5 < \log M_{200,c} < 14.0$) from a cosmological 
    simulation where the \mden{} profiles of galaxies are calculated using the 
    particle-tagging technique (e.g., \citealt{Cooper2010}). 
    The simulated \mden{} profile is affected by the resolution limit of the simulation in the inner region, but  is in good agreement with our median \mden{} profile for 
    the $11.6 <$ \logmtot{} $< 11.8$ bin within 40 kpc. 
    However, outside 40 kpc, the particle tagging method seems to predict a too 
    prominent stellar halo and has much shallower outer slope compared to our data. In future work, we will compare  our HSC profiles with  predictions from more advanced 
    hydrodynamic simulations such as XXX AND XXXXX. These data will help fine-tune simulations and to understand the physical mechanisms that drive the assembly of massive galaxies and the 
    build up of stellar halos.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_ell_color.pdf}
      \caption{\alexie{Remake the light grey lines in this figure. Pick a smaller number. Say 100. And make the thin grey lines a little darker. Right now it is really hard to get anything useful from the think grey lines.}
          Radial profiles of the ellipticty and optical colors of massive galaxies in our sample. The general format of this figure is similar to Fig~\ref{fig:avg_prof}.  The
          \textbf{left panel} displays ellipticity profiles, 
          the \textbf{Upper-right panel} shows $g-r$ color profiles, and  the
          \textbf{lower-right panel} is for $g-i$ color profiles. 
          We compare our results with those from (1) \citet{Tal2011} based on stacking 
          large samples of luminous red galaxies in SDSS at $z{\sim} 0.4$ 
          (solid red line on the left panel), 
          (2) the results from a stacking analysis of nearby massive 
          galaxies with high concentration index ($C>2.6$) in 
          \citet[][blue dash lines on the left and upper-right panels]{DSouza2014}, 
          (3) and the average $g-r$ and $g-i$ color profiles 
          from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
          lines on both right panels]{LaBarbera2010}.
          For color profiles, we also compare with deep observations of a few nearby 
          massive ETGs: the $g-r$ color profiles of NGC 4472 (\citealt{Mihos2013}) 
          and NGC 4365 (\citealt{Mihos2017}), and the $g-i$ profile of NGC 1399 
          (\citealt{Iodice2016}). \rachel{State explicitly that these are rest-frame colors.}
          }
      \label{fig:ell_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

	This is consistent with studies of nearby massive galaxies, both from 1-D 
	ellipticity profiles and 2-D modeling results \citep{Porter1991, Gonzalez2005, 
	Zibetti2005, Spavone2017; Huang2013a, Oh2017}. However,  to the best of our knowledge, our HSC results are the first to show  clear evidence that:  a) the ellipticities of the stellar halo  depend strong ly on galaxy mass, and b)  the ellipticity of the stellar halo is anti-correlated with the slope of \mden{}.

@@

    Regarding the color profiles, it is well known that massive elliptical galaxies 
    have shallow and negative color gradients that reflect radial variations in their  
    stellar populations (e.g.\ \citealt{Carollo1993, LaBarbera2012}) and hence contain
    information about the assembly history of their stellar halos (e.g. 
    \citealt{Hirschmann2015}). 
    The right panels of Fig \ref{fig:ell_color} show the $k$-corrected $g-r$ and 
    $g-i$ color profiles for all galaxies in our sample, together with the median profiles in three \mtot{} bins. We find the the  median $g-r$ and $g-i$ color  decreases  at larger radii, but there does not appear to be an significant mass dependence in the  gradient of the color profiles. We also compare our results with the stacked color profiles from  \citealt{LaBarbera2010}\footnote{We use the median color profiles of high-mass 
    ETGs; the original profile is in units of $R_{\mathrm{e}}$, we use a typical 
    $R_{\mathrm{e}}=8.0$ kpc to convert it into physical kpc} and 
    \citealt{DSouza2014}.
    The median color profiles from HSC images are systematically steeper than the 
    stacked SDSS ones. 
    Considering differences in the response curves between HSC and SDSS filters, together with the uncertainties of color measurements, the HSC $g-r$ color profiles are  in failry good agreement with  those from SDSS. However, the $g-i$ profiles of HSC galaxies are steeper compared to SDSS. The SDSS $i$-band suffers from the so-called ``red-halo'' effect
    (e.g. \citealt{Wu2005}, \citealt{Tal2011}).  This is due to  the fact that the SDSS $i$-band PSF has more prominent wing than other bands. Because the PSF model does not capture these wings, this artificially distributes more flux to the outskirts, and leads to apparently redder colors in 
    the low surface brightness outskirts of galaxies. Because HSC uses thick CCDs, HSC $i$-band images do not suffer from this effect and can be used to determine galaxy colors with higher accuracy.

@@

    Fairly steep color profiles have been observed in several very nearby massive 
    ETGs.  Fig \ref{fig:ell_color} shows the $g-r$ color profiles of 
    NGC 4472 (\citealt{Mihos2013}) and NGC 4365 (\citealt{Mihos2017})\footnote{
    Both are converted from $B-V$ colors}, and the $g-i$ profile of NGC 1399 
    (\citealt{Iodice2016}). These individual profiles  display  similar color gradients as our HSC sample.

@@

    State of the art hydrodynamic simulations of massive galaxy formation predict 
    that the fraction of accreted stars should strongly increase with stellar 
    mass and that for very massive galaxies, the  ``ex-situ'' may reach up to xxxxxxx \% of the total galaxy mass (e.g.
    \citealt{Oser2010, Cooper2013, Dubois2013, LeeYi2013, Hirschmann2015,
    RodriguezGomez2016}).

    This picture is supported by our observations that massive galaxies display more prominent stellar halos as well as by their  negative color gradients. The fact that the outskirts of these galaxies are slighly bluer than  the inner regions, is  consistent with the picture that  stellar halos are built up from  less massive galaxies \alexie{justify here. Why bluer?}.

@@

    For more massive ETGs,  results so far mainly depend on multi-component model fitting
    and image stacking analyses (e.g. \citealt{Huang2013a, dSouza2014, Spavone2017}).
    In this work, we propose that \mstar{} computed within different fixed physical apertures are worth exploring as  proxies of the  ex situ fraction. We propose to use the mass within 10 kpc (\minn{}) and 100 kpc (\mtot{}) as proxies for the \textit{in situ} componnt and for the total \mstar{}.

    On the left panel of Fig \ref{fig:discussion_1} we show the relation between \mtot{} and the fraction of mass between 10 and 100 kpc (as a proxy of the mass of the accreted component). We compare this with the  fraction of ex-situ stars predicted by the Illustris simulation 
    (\citealt{RodriguezGomez2016}).  We find that  our proxy for the accreted mass component correlates strongly with  \mtot{} and that this relation is surprisingly consistent with predictions from \citet{RodriguezGomez2016}.  Given the limitations of the Illustris simulation, and the impperfect nature of our proxy for the ex sity fraction proxy, the almost perfect agreeement seen in Figure \ref{fig:discussion_1} may well be a coincidence.  However, it is encouraging to see that our simple proxy for the fraction of ex sity stars seems to match both the slope and the scatter of the predicted relation.  There exist other  hydrodynamic simulations that predict significantly different ex situ fractions compared to Illustris (e.g. 
    \citealt{Lackner2012, Qu2017}).  In future work, we will explore more detailed comparisons between our data and predictions from hydrodynamic simulations and we will  investigate to what degree simple aperture masses may be used to  trace \textit{ex situ} fractions.

@@

%% ------------------------------------------------------------------------------------ %% 
\section{A. Extraction of 1-D surface brightness profile} 
    \label{app:ellipse}

@@

%% ------------------------------------------------------------------------------------ %% 
\section{B. Estimate average {$M_{\star}/L_{\star}$} using \texttt{iSEDFit}} 
    \label{app:sed}

>>>>

\def\etal{{\ et al.~}}
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}
\def\redm{\texttt{redMaPPer}}
\def\cmodel{\texttt{cModel}}
% Samples
\def\rbcg{\texttt{cenHighMh}}
\def\nbcg{\texttt{cenLowMh}}
\def\redbcg{{$\lambda \ge 30$}}
\def\nonbcg{{$\lambda < 20$}}
% Mass related 
\def\mstar{{$M_{\star}$}}
\def\mhalo{{$M_{\mathrm{200b}}$}}
\def\logms{{$\log (M_{\star}/M_{\odot})$}}
\def\logmh{{$\log (M_{\mathrm{200b}}/M_{\odot})$}}

@@

    With the help of the Stripe82 Massive Galaxy Catalog (\texttt{S82-MGC},
    \citealt{Bundy2015}
    )\footnote{http://www.ucolick.org/\~{}kbundy/massivegalaxies/s82-mgc.html}, 
    we investigate the \mstar{} completeness of our samples. 
    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the United 
    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; 
    \citealt{Lawrence2007}). 
    Comparing to normal SDSS images, the deeper photometry and better photo-$z$s 
    from \texttt{S82-MGC} make this sample complete to \logms{}$\geq 11.2$ at $z<0.7$ 
    which makes it sufficient to evaluate the completeness of our HSC sample.   
	By comparing with the \texttt{S82-MGC} sample (\citealt{Bundy2015}), 
	\citet{Leauthaud2016} have measured the \mstar{} completeness of the combined BOSS 
	and SDSS samples. 
    They estimate that the BOSS spec-$z$ sample, which is the main source of redshifts 
    for our sample, is about 80\% complete at 
    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. The GAMA survey is 80\% complete down to 
    $10^{10.8}$\msun{} at $z{\sim} 0.3$, but is only 80\% complete to 
    $10^{12.0}$\msun{} at $z{\sim} 0.5$ according to \citet{Taylor2011} (e.g.\ 
    their Fig.~6).

@@

    We use \texttt{v5.10} of the \redm{} cluster  catalog
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
    These authors have developed a well-tested red-sequence cluster finder that has 
    been run on SDSS DR8 (\citealt{SDSSDR8}) images. 
    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
    their associated membership probabilities. 
    Details about the performance of the \redm{}~cluster catalog can be found in 
    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}.

    Several studies have published calibrations between the \redm{}~richness estimate, 
    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
    Melchior2016}). 
    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
    Therefore the central galaxies of these \redm{} clusters\footnote{We only use 
    central galaxies with $P_{\mathrm{CEN}} \geq 0.7$} form a sample of massive central 
    galaxies that live in massive halos as described above.
\rachel{Intrinsic scatter in \mhalo{} at fixed $\lambda$ is pretty big, though, so we should be careful about this assertion.}
Such information is also very useful in studying the relationship between galaxy
    structure and environment (Huang\etal in prep.).
%% ------------------------------------------------------------------------------------ %%

@@

    As the next step, we want to construct a sample of central galaxies living in halos 
    with \logmh{}$<14.0$. 
    To achieve this, we identify and remove all galaxies within a cylindrical region 
    around all \redm{} clusters. 
    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
    set to twice the value of the photometric redshift uncertainty of each cluster.

    We convert $\lambda$ of each cluster to $M_{\mathrm{200b}}$ using the calibration 
    of \citet{Simet2016} and we use the mass-concentration relation from 
    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. 
    At $0.3 < z < 0.5$, the uncertainty of photo-$z$ is between 0.015 to 0.025, and 
    is enough to exclude cluster members.

    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
    in our sample will be dominated by central galaxies living in halos with 
    \logmh{}$< 14.0$. 
    We will refer to this sample of \textbf{galaxies in less 
    massive halos} as the \nbcg{} sample. Because we have rejected satellites in \redm{} clusters, and because above our galaxy mass cut most satellites reside in halos with \logmh$>14.0$ (e.g. \citealt{Reid2014, 
    Hoshino2015, Saito2016, vanUitert2016}), galaxies in the \nbcg{} sample should  be dominated by central galaxies.
    \rachel{There is a statistical distribution of halo masses that satellites at this stellar mass live in, based on the papers you cited; can you say more quantitatively what fraction you expect to be satellites in less massive halos?  Right now it all sounds kind of hand-wavey.}

@@

In this paper, we have only measured light profiles for central galaxies. Also,  we cannot extract  a 1-D profile for $\sim 11$\% of galaxies (because contamination from neighbouring galaxies is too severe). These two effects will lead to a ${\sim}20$\% uncertainty in  the amplitude of our SMF.  \rachel{Mass-dependent, or really 20\% at all masses?} These are limitations that we are currently working to address and a forthcoming paper will  address them. Our goal in this paper is therefore not  to  attempt a detailed comparison between different SMFs
    \citep[e.g.,][]{Bernardi2013, Bernardi2017}. Instead, our goal in this section is more simply to characterize the  impact of various \mstar{} measurements  on the high-mass end of the SMF.

@@

        \item The SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
            \citep{Leauthaud2016} where \mstar{} is derived using 
            \texttt{iSEDfit} on PSF-corrected aperture photometry from 
            \texttt{S82}. They adopt the same IMF, dust model, and star-formation model as we do, but use the \texttt{BC03} model. Based on the test results from Appendix \ref{app:sed}, we shift the \citet{Leauthaud2016} SMF by 0.08 dex to add their data to Figure~\ref{fig:smf}.      
        \item The SMF derived from a SDSS-\textit{GALEX} sample of $z{\sim} 0.1$ 
            galaxies from \citet{Moustakas13}.  Total luminosities from \citet{Moustakas13} are based on SDSS \cmodel{} magnitude. 
            They use a \m2l{} that is derived via SED fitting using \texttt{iSEDfit} with similar 
            assumptions as here.
        \item The observed SMF for $z{\sim} 0.1$ SDSS galaxies from 
            \citet{Bernardi2017}.  Total luminosities in  \citet{Bernardi2017} are based on 2-D \texttt{SerExp} models 
            (\ser{}$+$ Exponential disk model; integrated to infinity) that 
            recover more flux compared to SDSS \cmodel{} magnitudes 
            (\citealt{Bernardi2013, Meert2015}). 
            They use a \m2l{} that is adopted from the SED fitting results from the ``dusty'' 
            model in \citet{Mendel2014}. 
            This model also uses the \texttt{FSPS} stellar population model 
            \citep{FSPS} and assumes a \citet{Chabrier2003} IMF. 
    \end{itemize}

@@

    Finally, we also compare with the predicted median \mden{} profile of central 
    galaxies in massive halos ($13.5 < \log M_{200,c} < 14.0$) from a cosmological 
    simulation where the \mden{} profiles of galaxies are calculated using the 
    particle-tagging technique (e.g., \citealt{Cooper2010}). 
    The simulated \mden{} profile is affected by the resolution limit of the simulation in the inner region, but  is in good agreement with our median \mden{} profile for 
    the $11.6 <$ \logmtot{} $< 11.8$ bin within 40 kpc. 
    However, outside 40 kpc, the particle tagging method seems to predict a too 
    prominent stellar halo and has much shallower outer slope compared to our data. In future work, we will compare  our HSC profiles with  predictions from more advanced 
    hydrodynamic simulations such as Horizon-AGN () and MassiveBlackII (). These data will help fine-tune simulations and to understand the physical mechanisms that drive the assembly of massive galaxies and the 
    build up of stellar halos.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_ell_color.pdf}
      \caption{
          Radial profiles of the ellipticty and $k$-corrected rest-frame optical colors 
          of massive galaxies in our sample. 
          The general format of this figure is similar to Fig~\ref{fig:avg_prof}.  
          The \textbf{left panel} displays ellipticity profiles, 
          the \textbf{Upper-right panel} shows $g-r$ color profiles, and  the
          \textbf{lower-right panel} is for $g-i$ color profiles. 
          We compare our results with those from (1) \citet{Tal2011} based on stacking 
          large samples of luminous red galaxies in SDSS at $z{\sim} 0.4$ 
          (solid red line on the left panel), 
          (2) the results from a stacking analysis of nearby massive 
          galaxies with high concentration index ($C>2.6$) in 
          \citet[][blue dash lines on the left and upper-right panels]{DSouza2014}, 
          (3) and the average $g-r$ and $g-i$ color profiles 
          from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
          lines on both right panels]{LaBarbera2010}.
          For color profiles, we also compare with deep observations of a few nearby 
          massive ETGs: the $g-r$ color profiles of NGC 4472 (\citealt{Mihos2013}) 
          and NGC 4365 (\citealt{Mihos2017}), and the $g-i$ profile of NGC 1399 
          (\citealt{Iodice2016}).
          }
      \label{fig:ell_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

	This is consistent with studies of nearby massive galaxies, both from 1-D 
	ellipticity profiles and 2-D modeling results \citep{Porter1991, Gonzalez2005, 
	Zibetti2005, Spavone2017, Huang2013a, Oh2017}. However,  to the best of our knowledge, our HSC results are the first to show  clear evidence that:  a) the ellipticities of the stellar halo  depend strongly on galaxy mass, and b)  the ellipticity of the stellar halo is anti-correlated with the slope of \mden{}.

@@

    Regarding the color profiles, it is well known that massive elliptical galaxies 
    have shallow and negative color gradients that reflect radial variations in their  
    stellar populations (e.g.\ \citealt{Carollo1993, LaBarbera2012}) and hence contain
    information about the assembly history of their stellar halos (e.g. 
    \citealt{Hirschmann2015}). 
    The right panels of Fig \ref{fig:ell_color} show the $k$-corrected $g-r$ and 
    $g-i$ color profiles for all galaxies in our sample, together with the median profiles in three \mtot{} bins. We find the the  median $g-r$ and $g-i$ color  decreases  at larger radii, but there does not appear to be an significant mass dependence in the  gradient of the color profiles. We also compare our results with the stacked color profiles from  \citealt{LaBarbera2010}\footnote{We use the median color profiles of high-mass 
    ETGs; the original profile is in units of $R_{\mathrm{e}}$, we use a typical 
    $R_{\mathrm{e}}=8.0$ kpc to convert it into physical kpc.} and 
    \citealt{DSouza2014}.
    The median color profiles from HSC images are systematically steeper than the 
    stacked SDSS ones. 
    Considering differences in the response curves between HSC and SDSS filters, together with the uncertainties of color measurements, the HSC $(g-r)$ color profiles are  in fairly good agreement with  those from SDSS. However, the $(g-i)$ profiles of HSC galaxies are steeper compared to SDSS. The SDSS $i$-band suffers from the so-called ``red-halo'' effect
    (e.g. \citealt{Wu2005}, \citealt{Tal2011}).  This is due to  the fact that the SDSS $i$-band PSF has more prominent wing than other bands. Because the PSF model does not capture these wings, this artificially distributes more flux to the outskirts, and leads to apparently redder colors in 
    the low surface brightness outskirts of galaxies. Because HSC uses thick CCDs, HSC $i$-band images do not suffer from this effect and can be used to determine galaxy colors with higher accuracy.

@@

    Fairly steep color profiles have been observed in several very nearby massive 
    ETGs.  Fig \ref{fig:ell_color} shows the $g-r$ color profiles of 
    NGC 4472 (\citealt{Mihos2013}) and NGC 4365 (\citealt{Mihos2017})\footnote{
    Both are converted from ($B-V$) colors.}, and the $g-i$ profile of NGC 1399 
    (\citealt{Iodice2016}). These individual profiles  display  similar color gradients as our HSC sample.

@@

    State of the art hydrodynamic simulations of massive galaxy formation predict 
    that the fraction of accreted stars should strongly increase with stellar 
    mass and that for very massive galaxies, the \textit{ex-situ} may reach up to 
    50-90\% of the total galaxy mass (e.g.
    \citealt{Oser2010, Cooper2013, Dubois2013, LeeYi2013, Hirschmann2015,
    RodriguezGomez2016}).

    This picture is supported by our observations that massive galaxies display more 
    prominent stellar halos as well as by their  negative color gradients. 
    The fact that the outskirts of these galaxies are slightly bluer than the inner
    regions, is consistent with the picture that stellar halos are built up by 
    series of minor mergers (average merger mass-ratio between 1:3-1:10; e.g. 
    \citealt{Huang2016}) as less massive ETGs are typically bluer.

@@

    For more massive ETGs,  results so far mainly depend on multi-component model fitting
    and image stacking analyses (e.g. \citealt{Huang2013a, DSouza2014, Spavone2017}).
    In this work, we propose that \mstar{} computed within different fixed physical apertures are worth exploring as  proxies of the  ex situ fraction. We propose to use the mass within 10 kpc (\minn{}) and 100 kpc (\mtot{}) as proxies for the \textit{in situ} component and for the total \mstar{}.

    On the left panel of Fig \ref{fig:discussion_1} we show the relation between \mtot{} and the fraction of mass between 10 and 100 kpc (as a proxy of the mass of the accreted component). We compare this with the  fraction of ex-situ stars predicted by the Illustris simulation 
    (\citealt{RodriguezGomez2016}).  We find that  our proxy for the accreted mass component correlates strongly with  \mtot{} and that this relation is surprisingly consistent with predictions from \citet{RodriguezGomez2016}.  Given the limitations of the Illustris simulation, and the imperfect nature of our proxy for the ex situ fraction proxy, the almost perfect agreement seen in Figure \ref{fig:discussion_1} may well be a coincidence.  However, it is encouraging to see that our simple proxy for the fraction of ex situ stars seems to match both the slope and the scatter of the predicted relation.  There exist other  hydrodynamic simulations that predict significantly different ex situ fractions compared to Illustris (e.g. 
    \citealt{Lackner2012, Qu2017}).  In future work, we will explore more detailed comparisons between our data and predictions from hydrodynamic simulations and we will  investigate to what degree simple aperture masses may be used to trace \textit{ex situ} fractions.

@@

%% ------------------------------------------------------------------------------------ %%  
\section{A. Basic Statistical Properties of the Sample} 
	\label{app:basic}

    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-color 
    relations using the $k$-corrected $g-r$ color. 
    Both samples follow the same tight ``red-sequence'' with little contamination 
    from the ``blue cloud''.
    At fixed \mtot{}, we see little offset in color distributions of the two 
    samples, suggesting that both samples consist of quiescent galaxies with 
    similar average stellar population properties.  
    This is consistent with previous result that suggests the average stellar 
    population of massive central galaxy does not depend on \mhalo{} 
    (e.g.\ \citealt{Park2007}).  
    In this work, we focus on the \mstar{} range of $11.6 \le$\logmtot{}$\le 11.9$, 
    where both samples have acceptable completeness, and their \mtot{} distributions 
    greatly overlap (see the normalized distributions of \mtot{} in the bottom-left 
    panel of Fig~\ref{fig:sample_stats}). 
    As for the \minn{} distributions, the two samples overlap the most within 
    $11.2 \le$\logmtot{}$\le 11.6$, but now they show quite different
    distributions (bottom-right figure).

    The redshift distributions also show small difference
    (upper-right panel) even in the high-\mtot{} bin, where the redshift distribution 
    of the \nbcg{} sample skews toward higher-$z$ end due to the contribution of BOSS 
    spec-$z$.

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure}
      \centering 
      \includegraphics[width=\columnwidth]{fig/redbcg_sample_stats}
      \caption{
          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
          (red circle; detaield format is the same with the right panel of 
          Fig~\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
          mass bins.
          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
          $0.3 \leq z \leq 0.5$ (stepped histogram). 
          The vertical lines in both top-left and bottom-left figures highlight the 
          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
          the \mtot{}-matched samples.~~
          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
          Here the vertical lines highlight the 
          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
      }
      \label{fig:sample_stats}
  \end{figure}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{B. Extraction of 1-D surface brightness profile} 
    \label{app:ellipse}

@@

%% ------------------------------------------------------------------------------------ %% 
\section{C. Estimate average {$M_{\star}/L_{\star}$} using \texttt{iSEDFit}} 
    \label{app:sed}
